%----------------------------------------------------------------------------------------
%   acortino — Senior Software Engineer resume
%----------------------------------------------------------------------------------------
\documentclass[10pt,a4paper]{article}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{raleway}
\renewcommand*\familydefault{\sfdefault}

\usepackage[a4paper,top=1cm,bottom=1cm,left=1.2cm,right=1.2cm,footskip=0.8cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage[final]{microtype}
\usepackage{xcolor}
\usepackage{pagecolor}
\usepackage{enumitem}
\usepackage[most]{tcolorbox}
\usepackage{fontawesome}
\usepackage{worldflags}
\usepackage{fancyhdr}
\usepackage{ragged2e}

%----------------------------------------------------------------------------------------
%   COLORS
%----------------------------------------------------------------------------------------
\definecolor{cvbg}{HTML}{F9F9EC}
\definecolor{cvtext}{HTML}{141414}
\definecolor{cvmute}{HTML}{6B6B6B}
\definecolor{cvsoft}{HTML}{B5ADA5}
\definecolor{cvline}{HTML}{E8E4DF}
\definecolor{cvaccent}{HTML}{26B9A4}
\definecolor{cvpink}{HTML}{FC0096}

\pagecolor{cvbg}
\color{cvtext}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

%----------------------------------------------------------------------------------------
%   PAGE STYLE
%----------------------------------------------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\thepage}{}
\fancyfoot[C]{\scriptsize\textcolor{cvsoft}{Last update: May 2026}}

\fancypagestyle{plain}{%
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
  \fancyfoot[C]{\scriptsize\textcolor{cvsoft}{Last update: May 2026}}
}

%----------------------------------------------------------------------------------------
%   BASICS
%----------------------------------------------------------------------------------------
\newcommand{\pink}[1]{\textcolor{cvpink}{\textbf{#1}}}
\newcommand{\muted}[1]{\textcolor{cvmute}{#1}}
\newcommand{\sectiongap}{\vspace{15pt}}

\newcommand{\cvsect}[1]{%
  {\small\textcolor{cvaccent}{\MakeUppercase{\textbf{#1}}}}\\[-0.2em]
  \textcolor{cvaccent}{\rule{\linewidth}{1pt}}\\[0.4em]
}

\newcommand{\icon}[2]{%
  \colorbox{cvaccent}{\makebox(#2,#2){\textcolor{cvbg}{\large\csname fa#1\endcsname}}}%
}

\newcommand{\icontext}[3]{%
  \icon{#1}{#2}\hspace{0.25cm}\textcolor{cvtext}{#3}%
}

%----------------------------------------------------------------------------------------
%   LISTS
%----------------------------------------------------------------------------------------
\newlist{cvbullets}{itemize}{1}
\setlist[cvbullets]{%
  label=\raisebox{0.2ex}{\textcolor{cvaccent}{\rule{0.65ex}{0.65ex}}},
  leftmargin=1.1em,
  labelsep=0.55em,
  itemsep=1.5pt,
  topsep=2pt,
  parsep=0pt,
  partopsep=0pt
}

%----------------------------------------------------------------------------------------
%   CARDS
%----------------------------------------------------------------------------------------
\tcbset{
  cvcard/.style={
    enhanced,
    colback=cvbg,
    colframe=cvline,
    boxrule=0.55pt,
    arc=2mm,
    left=3mm,
    right=3mm,
    top=2.2mm,
    bottom=2.2mm,
    boxsep=0pt,
    before skip=0pt,
    after skip=0pt
  }
}

\newcommand{\skillcard}[3]{%
  \begin{tcolorbox}[cvcard]
    {\small\pink{\MakeUppercase{#1}}}%
    \hfill
    {\scriptsize\textcolor{cvaccent}{#2}}%
    \par\vspace{1.8mm}
    {\small #3}
  \end{tcolorbox}%
}

\newcommand{\entrycard}[4]{%
  \begin{tcolorbox}[cvcard,width=\linewidth]
    \begin{minipage}[t]{0.19\linewidth}
      {\footnotesize\textcolor{cvmute}{#1}}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.77\linewidth}
      {\textcolor{cvaccent}{\textbf{#2}}}%
      \hfill
      {\small\pink{\textbf{#3}}}
      \par\vspace{1.7mm}
      #4
    \end{minipage}
  \end{tcolorbox}
  \vspace{2.2mm}
}

\newcommand{\smallcard}[2]{%
  \begin{tcolorbox}[cvcard]
    {\small\pink{\MakeUppercase{#1}}}
    \par\vspace{1.8mm}
    {\small #2}
  \end{tcolorbox}%
}

%----------------------------------------------------------------------------------------
%   TECH PILLS
%----------------------------------------------------------------------------------------
\newcommand{\tech}[1]{%
  \tcbox[
    on line,
    colback=cvbg,
    colframe=cvline,
    boxrule=0.4pt,
    arc=1.5mm,
    left=1mm,
    right=1mm,
    top=0.45mm,
    bottom=0.45mm,
    boxsep=0pt
  ]{\scriptsize\texttt{\textcolor{cvmute}{#1}}}%
}

\newcommand{\techline}[1]{%
  \par\vspace{2mm}%
  {\raggedright #1\par}%
}


%----------------------------------------------------------------------------------------
%   DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\small

%----------------------------------------------------------------------------------------
%   HEADER
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.67\textwidth}\hrule height 0pt width 0pt%
    {\Huge\textbf{Hello, I’m \pink{acortino}.}}\\[-0.1em]
    {\Large Senior Software Engineer}\\[0.45em]
    \textcolor{cvmute}{I build backend and real-time systems under production constraints.}
  \end{minipage}%
  \hfill
  \begin{minipage}[t]{0.30\textwidth}\hrule height 0pt width 0pt%
    \small
    \icontext{MapMarker}{12}{Strasbourg, France}\\
    \icontext{At}{12}{\href{mailto:hello@acortino.me}{hello@acortino.me}}\\
    \icontext{Globe}{12}{\href{https://acortino.me}{acortino.me}}\\
    \icontext{Linkedin}{12}{\href{https://linkedin.com/in/acortino}{linkedin.com/in/acortino}}
  \end{minipage}%
  \par\vspace{6pt}
  \textcolor{cvline}{\rule{\linewidth}{1pt}}
  \vspace{6pt}

%----------------------------------------------------------------------------------------
%   PROFILE
%----------------------------------------------------------------------------------------
\cvsect{Profile}
I’m a software engineer focused on backend and distributed systems. Most of my work has been around real-time processing, APIs, streaming pipelines, and integrating AI workloads into production systems. I like simplifying systems, reducing operational friction, and iterating through real-world constraints such as latency, reliability, and scale.

\sectiongap

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------
\cvsect{Skills}
\begin{minipage}[t]{0.48\textwidth}
  \skillcard{Core}{Daily / production}{
 \texttt{Java} • \texttt{Python} • \texttt{SQL} \\[1mm]
  \texttt{Spring Boot} • \texttt{Kafka} • \texttt{gRPC} \\[1mm]
  \texttt{PostgreSQL} • \texttt{REST APIs} • \texttt{WebSocket}
  }
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
  \skillcard{Familiar with}{Used / comfortable}{
    \texttt{Angular} • \texttt{TypeScript} • \texttt{FastAPI} • \texttt{Django} \\
    \texttt{AWS} • \texttt{Kubernetes} • \texttt{OpenTofu/Terraform} • \texttt{Helm} \\
    \texttt{Auth0/SCIM} • \texttt{Github Actions}
  }
\end{minipage}

\sectiongap

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------
\cvsect{Experience}

\entrycard
{Jan. 2026 -- Present\\Ongoing\\Strasbourg, FR}
{Sr. Software Engineer}
{Independent Project}
{
  \muted{Building a medical workflow application around transcription, reporting, and AI-assisted image analysis.}

  \begin{cvbullets}
    \item Built backend services for patient case management, report generation, and resumable workflows.
    \item Implemented a real-time transcription pipeline using WebSocket, Java, gRPC, and Python/Whisper.
    \item Integrated external AI services for segmentation and prediction through Python gRPC workers.
    \item Built deployment infrastructure on AWS/Kubernetes using OpenTofu and Helm.
  \end{cvbullets}

  \techline{\tech{Spring Boot} \tech{Angular} \tech{Python} \tech{gRPC} \tech{AWS} \tech{CI/CD}}
}

\entrycard
{Feb. 2023 -- Jan. 2026\\3 years\\Palo Alto, CA, USA}
{Sr. Software Engineer}
{Uniphore}
{
  \muted{Worked on real-time AI systems for sales intelligence products.}

  \begin{cvbullets}
    \item Owned a Python service for real-time sentiment analysis integrated into a Kafka/gRPC microservice pipeline.
    \item Reduced end-to-end latency by 84\% by replacing file-based exchange with chunked streaming.
    \item Reduced memory usage by 70\% in a core Java service using streaming buffers.
    \item Built a SCIM synchronization service between Okta/AD, Auth0, and internal systems.
  \end{cvbullets}

  \techline{\tech{Spring Boot} \tech{Python} \tech{Kafka} \tech{gRPC} \tech{SCIM}}
}

\entrycard
{Aug. 2020 -- Feb. 2023\\2.6 years\\Strasbourg, FR}
{Software Engineer}
{Hexagone Behavioral Technology}
{
  \muted{Worked on multimodal emotion analysis systems processing voice, facial, and text data in real time.}

  \begin{cvbullets}
    \item Built low-latency streaming services for audio sentiment analysis using Kafka and WebSocket.
    \item Integrated ML models into production services with validation and fallback handling.
    \item Contributed to deployment and monitoring on OpenShift environments.
  \end{cvbullets}

  \techline{\tech{Python} \tech{Django} \tech{Kafka} \tech{OpenShift} \tech{Angular}}
}

\entrycard
{Mar. 2018 -- Jul. 2020\\2.3 years \\Strasbourg, FR}
{Software Engineer}
{Oxycar}
{
  \muted{Worked on cross-platform mobile applications for carpooling services.}

  \begin{cvbullets}
    \item Maintained iOS and Android applications built with Angular and NativeScript.
    \item Integrated messaging, geolocation, and payment systems.
    \item Built CI/CD pipelines for App Store and Google Play releases.
  \end{cvbullets}

  \techline{\tech{Angular} \tech{TypeScript} \tech{NativeScript} \tech{Mobile}}
}

\entrycard
{Sep. 2016 -- Mar. 2018\\1.6 years \\Belfort, FR}
{Software Engineer \textit{(Co-founder)}}
{Blueanthill}
{
  \muted{Built analytics tools around large-scale social media datasets during the 2017 French presidential campaign.}

  \begin{cvbullets}
    \item Built data ingestion and search services using Node.js and Elasticsearch.
    \item Processed and indexed more than 20M tweets.
    \item Developed dashboards for real-time exploration and visualization.
  \end{cvbullets}

  \techline{\tech{Node.js} \tech{AngularJS} \tech{Elasticsearch}}
}

\entrycard
{Sep. 2013 -- Sep. 2016\\3 years\\Montbéliard, FR}
{Software Engineer \textit{(Apprentice)}}
{Segula Technologies}
{
  \muted{Developed internal engineering tools and simulation software for automotive projects.}

  \begin{cvbullets}
    \item Built automation tools around CATIA workflows.
    \item Developed a thermal simulation tool for automotive A/C systems.
    \item Contributed to a prototype in-car interface presented at the Geneva Auto Show.
  \end{cvbullets}

  \techline{\tech{C++} \tech{Delphi} \tech{CATIA}}
}

\entrycard
{Mar. 2013 -- Jul. 2013\\0.4 years\\Belfort, FR}
{Web Developer \textit{(Intern)}}
{Trinaps}
{
  \muted{Built internal web tools and deployed network access solutions in real-world environments.}

  \begin{cvbullets}
    \item Developed internal Django web tools.
    \item Helped deploy a captive portal system for Les Eurockéennes festival.
  \end{cvbullets}

  \techline{\tech{Python} \tech{Django}}
}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\sectiongap
\cvsect{Education}

\entrycard
{2013 -- 2016\\Montbéliard, FR}
{Engineering Degree}
{Université de Belfort Montbéliard}
{Computer Science — Information Systems}

\entrycard
{2012 -- 2013\\Belfort, FR}
{Bachelor’s Degree \textit{(Licence)}}
{IUT Belfort Montbéliard}
{Web \& Mobile Development — System Administration}

\entrycard
{2007 -- 2013\\Belfort, FR}
{DUT \textit{(BTEC Higher National Diploma)}}
{IUT Belfort Montbéliard}
{Computer Science}

%----------------------------------------------------------------------------------------
%   OUTSIDE WORK
%----------------------------------------------------------------------------------------
\sectiongap
\cvsect{Outside Work}

\begin{minipage}[t]{0.31\textwidth}
  \smallcard{Reading}{
    \muted{Emil Cioran • Daniel Quinn • Albert Camus • George Orwell • Chuck Palahniuk • Luke Rhinehart • Noam Chomsky • Chinese classics}
  }
\end{minipage}%
\hfill
\begin{minipage}[t]{0.31\textwidth}
  \smallcard{Interests}{
    \muted{Animal behavior (evolution, biomimicry, edge-cases) • renovation • cooking • small automation tools}
  }
\end{minipage}%
\hfill
\begin{minipage}[t]{0.31\textwidth}
  \smallcard{Languages}{
    \muted{\worldflag[width=7,framewidth=0mm]{FR} \textit{(Native)} • \worldflag[width=7,framewidth=0mm]{GB} \textit{(Fluent)}}\\[1mm]
    \muted{Learning: \worldflag[width=7,framewidth=0mm]{IT} \textit{(B2)} • \worldflag[width=7,framewidth=0mm]{CN} \textit{(Beginner)} • \worldflag[width=7,framewidth=0mm]{ES} \textit{(Beginner)}}
  }
\end{minipage}

\end{document}
